\documentclass{report}
\usepackage{float}
\usepackage[english]{babel}
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\graphicspath{{images}}
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}
\title{Living life purely with crypto}

\author{Mr Ashlin Darius Govindasamy\\ \large{University of South Africa}}

\date{\today}

\begin{document}
\maketitle
\newpage

\tableofcontents
\pagenumbering{arabic} 

\chapter*{Introduction}
\input{chapters/introduction.tex}

\chapter{Crypto Wallets}
\input{chapters/cryptowallet.tex}

\chapter{Mining cryptocurrency (Generating passive income)}
\input{chapters/mining.tex}

\chapter{Taxation on cryptocurrencies}
\input{chapters/taxation.tex}

\chapter{Living life with crypto}
\input{chapters/livinglife.tex}

\chapter*{Conclusion}
I think that crypto is the future of finance. We will use it to gain freedom from the financial system. It is quite exciting to see how we can use crypto to do this. I think cryptocurrency is here to stay considering we have a huge Luno wallet skyscraper here says it all.
At the moment majority of people want to get rich over night with cryptocurrency. People dont understand the value of cryptocurrency. As the $t$ progresses i will be amazed to see what the future holds for cryptocurrency. For starting the crypto farm start small and progress yourself over $t$. That is my advice if you have cash problems. One card is good enough for starting to earn passive income with crypto. My golden rule of crypto dont buy it mine it.

\newpage

\end{document}