\subsection{Introduction to cryptocurrency wallets}
A cryptocurrency wallet is a software application that allows you to store and manage your cryptocurrency assets. \\

Consider the following example: \\

Your bank account has $x$ amount of money. The bank manages the money in your bank account. You can withdraw money from the bank account. Deposit money. Borrow money (Loan,Credit Card). Transfer money to other beneficiaries. Earn interest on your money. \\

Now consider the crypto wallet is your bank account/crypto asset. Some crypto wallet provides you with the ability to store and manage your cryptocurrency assets. Some wallets have different features. But all wallets satisfy you transferring/withdrawing crypto and depositing crypto. \\

\subsubsection{What is a software (hot) crypto wallet?}
Cryptocurrency software wallets enable crypto holders to securely store their digital currencies and tokens in one place. Cryptocurrency wallets often also allow users to buy, swap, lend and earn cryptocurrency, similar to how your bank account lets you access savings and loan products.

Now these wallets are software wallets. Meaning it is a computer program that you download and run on your computer. Your assets will be stored in some form of digital cloud exchange. Some software wallets store money on the device itself. \\

There have been cases were some digital exchange providers have been hacked and some assets/wallets have been stolen. There are some scam digital exchange providers out there. Make sure when you choose a good software wallet you do through research on picking a reputable exchange with the best security. Different brands of software wallets have different features and security also the user complexity of the software wallet is different throughout all. \\

Below is a list of software wallets I have tried that are available in the market.

\textbf{Example of Software Wallets}
\begin{enumerate}
\item Exodus
\item MetaMask
\item Crypto.com
\item Nicehash Exchange
\item Luno Wallet
\end{enumerate}

\textbf{Hot wallet advantages:}
    \begin{enumerate}
    \item Great for regular payments and micropayments;
    \item Convenient and easy to use;    
    \item Do not require physical media.
    \end{enumerate}
\textbf{Hot wallet disadvantages:}
    \begin{enumerate}
    \item Can be hacked more easily;
    \item Requires an Internet connection to work;
    \item If you uninstall the program, you may lose access to your cryptocurrency wallet forever.
    \end{enumerate}

\subsubsection{What is a hardware (cold) crypto wallet?}
A hardware wallet is a cryptocurrency wallet which stores the user's private keys (critical piece of information used to authorise outgoing transactions on the blockchain network) in a secure hardware device. The main principle behind hardware wallets is to provide full isolation between the private keys and your easy-to-hack computer or smartphone.
All the assets are stored in a secure hardware device and have no access to your computer or smartphone. \\

\textbf{Example of hardware wallets:}
\begin{enumerate}
\item Ledger Nano S
\item Trezor
\item KeepKey
\end{enumerate}

\textbf{Cold wallet advantages:}
\begin{enumerate}
    \item Higher security; with little to no software requirements and no connection to the Internet. \\
    \item No need to install any software. \\    
\end{enumerate}    

\textbf{Cold wallet disadvantages:}
\begin{enumerate} 
    \item Poorly adapted for regular payments.
    \item Requires a physical device to work.
    \item Can be physically lost since it’s stored on a piece of hardware;
    \item Requires manual backup.
    \item Requires a lot of time to setup and setup is not easy.
\end{enumerate}    

\subsection{What wallet should you be using?}

Consider the hardware wallets and software wallets. 

Hardware wallets should be used to store your main assets such as lump sum of crypto assets. 

Software wallets should be used for day to day transactions, automation projects and storing just the right amount in case of hacks on the exchange. You can never know what will happen in the world of hacking.

With some time in the future i will experiment making my own hardware wallet.







